251 MA

### 2022-12-13 code/process.Rmd
accomodate betas

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
```

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction"))

@@

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    partial_eta=(val*df_1)/(val*df_1+df_2)
    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
  }
  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df))
}
```

```{r}
parse_chisq <- function(chival, within_between){
  df=str_extract(chival, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  n=str_extract(chival, ",N=.*\\)") |> str_sub(4,-2) |> as.numeric()
  val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
  pval=pchisq(val,df, lower.tail=F)
  phi=sqrt(val/n)
  d_calc=NA
  if (!is.na(df)&&df==1){
    d_calc=esc_phi(phi,pval,n, es.type="d")$es
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n))
}

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))
}

@@

```{r}
parse_wilcoxon <- function(wilcox){
  z=str_sub(wilcox,11,-1) |> as.numeric()
  pval=pnorm(z,lower.tail=F)
  #r=z/sqrt(n)
  #d_calc=4*r/(sqrt(1-r**2))
  d_calc=NA
    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA))

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}

@@

@@

d_es_try <- d_es |> filter(!is.na(target_d_calc)) |> 
  filter(!is.na(rep_d_calc)) |> 
  mutate(
         predInt=Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
         p_orig=Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))

@@

d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
  geom_point()+
  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
  geom_abline(slope=1, intercept=0)+
  scale_color_viridis(discrete=T, direction=-1)

@@

d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
  select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
         -target_fstat, -target_tstat, -target_df_1, -target_df_2,
         -d_fill_rep, -d_fill_target, 
         -replication_ES_type, -replication_ES_value, -replication_pvalue,
         -target_ES_type, -target_ES_value, -target_pvalue,
         -rep_N_calc, -target_N_calc,
         -replication_test, -target_test) |> 
pivot_longer(everything()) |>
  arrange(desc(value)) |>
  filter(value!=0)

>>>>

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
```
We have maybe as many as 178 at least for some analyses.

Descriptions:

- "great" means we have all relevant cells coded in spreadsheet

- "ES_direction" is great except that we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)

- "stuck" means that I'm stuck somewhere -- we don't have everything filled in, but it may be possible to get there

- "hopeless" means we don't have everything filled in, but I don't believe filling in more/all is possible

- "TODO" means I'm still working on data coding (this year's projects)

```{r}
d_val <- d |> filter(!status %in% c("missing", "non-experiment", "reproduction", "TODO"))

@@

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    partial_eta=(val*df_1)/(val*df_1+df_2)
    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
  }
  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_chisq <- function(chival, within_between){
  df=str_extract(chival, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  n=str_extract(chival, ",N=.*\\)") |> str_sub(4,-2) |> as.numeric()
  val=str_extract(chival, "\\)=.*") |> str_sub(3,-1) |> as.numeric() |> abs()
  pval=pchisq(val,df, lower.tail=F)
  phi=sqrt(val/n)
  d_calc=NA
  if (!is.na(df)&&df==1){
    d_calc=esc_phi(phi,pval,n, es.type="d")$es
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=n, "beta"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))
}

@@

```{r}
parse_wilcoxon <- function(wilcox){
  z=str_sub(wilcox,11,-1) |> as.numeric()
  pval=pnorm(z,lower.tail=F)
  #r=z/sqrt(n)
  #d_calc=4*r/(sqrt(1-r**2))
  d_calc=NA
    return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "beta"=NA, "SE"=NA))

@@

parse_beta_se <- function(raw_stat){
    beta=str_extract(raw_stat, "b=.*\\(") |> str_sub(3,-2) |> as.numeric()
    se=str_extract(raw_stat, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
    zval=beta/se
    print(zval)
    pval=2*pnorm(zval, lower.tail=F)
return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=pval, "d_calc"=NA, "N_calc"=NA, "beta"=beta, "SE"=se))
}

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "beta"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="c"){return(parse_chisq(raw_stat, within_between))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}

@@

It may be worth checking points that are above the line.

@@

d_es_try <- d_es |> filter(!is.na(target_d_calc)&!is.na(rep_d_calc)|!is.na(target_beta)&!is.na(rep_beta)) |> 
  mutate(
         predInt=ifelse(!is.na(target_d_calc),
                        Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside,
                        Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside),
         p_orig=ifelse(!is.na(target_d_calc),
                       Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2),
                       Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2)))

@@

d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
  geom_point()+
  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
  geom_abline(slope=1, intercept=0)+
    geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)

@@

d_check_nas <- d_es |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
    select(-rep_fstat, -rep_tstat,-rep_df_1,-rep_df_2,
         -target_fstat, -target_tstat, -target_df_1, -target_df_2,
         -d_fill_rep, -d_fill_target, 
         -replication_ES_type, -replication_ES_value, -replication_pvalue,
         -target_ES_type, -target_ES_value, -target_pvalue,
         -rep_N_calc, -target_N_calc,
         -replication_test, -target_test)

d_check_nas |> summarize(                                                      across(everything(),~sum(is.na(.)))) |>
pivot_longer(everything()) |>
  arrange(desc(value)) |>
  filter(value!=0)

message("number of complete rows")

d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()
